### 2020-05-19 presentation.tex
presentation

\documentclass{f4_beamer}

\usepackage{iftex}
\ifPDFTeX
   \usepackage[utf8]{inputenc}
   \usepackage[T1]{fontenc}
   \usepackage{lmodern}
\else
   \ifXeTeX
     \usepackage{fontspec}
   \else 
     \usepackage{luatextra}
   \fi
   \defaultfontfeatures{Ligatures=TeX}
\fi

\title{Ethereum}
\subtitle{Transaktionen}
\author{Jannes Neemann, Ture Claußen}
\date{\today}

\begin{document}

\section{Überblick}

\begin{frame}{Überblick}

\end{frame}

\begin{frame}{Einführung 2}

\end{frame}

\section{Noch mehr Einführung}

\begin{frame}{Noch mehr Einführung}

\end{frame}

\begin{frame}{Noch mehr Einführung  usw.}

\end{frame}

\end{document}